\begin{tabularx}{\textwidth}{L R}
    \textit{University of Chicago, Center for Data Intensive Science} & Chicago, IL \\
    \small{Software Engineer} & \small{Jan. 2015 --- June 2016} \\
\end{tabularx}
\begin{tabularx}{\textwidth}{X}
    \begin{small}
    \begin{itemize}
        \itemsep\itemseppts
        \item[-] Full stack development, deployment, and maintenance of NIH NCI Genomic Data Commons (GDC) systems.
        \item[-] Assisted in development of in-house frameworks for deployment, management, and scaling of production bioinformatics systems. Scaled analysis pipelines to thousands of hosts across two OpenStack deployments.
        \item[-] Designed and prototyped UDT-based transport layer reverse proxy. Consistently achieved two fold increase in average throughput over cross-continental 100Gbps links vs raw TCP without modification of user applications.
        \item[-] Designed and implemented ranged request microservice for slicing BAM format bioinformatics objects.
        \item[-] Designed and implemented distributed RESTful identifier service for use in data co-location applications.
        \item[-] Diagnosed and fixed critical production failures, including ARP poisoning and Ceph object store corruption.
        \item[-] Designed and developed Python libraries and command line tools for the use and management of the Spectra Logic Black Pearl S3 tape backup solution. Identified and diagnosed critical data integrity issues of the Black Pearl system.
    \end{itemize}
    \end{small}
\end{tabularx}
