\begin{tabularx}{\textwidth}{L}
    \textbf{RECENT WORK EXPERIENCE}
\end{tabularx}

\begin{tabularx}{\textwidth}{L R}
    \normalsize\textit{Cellular Longevity, dba Loyal} & San Francisco, CA \\
    \hspace{10pt}Senior Data Engineer & September 2021 --- Current \\
\end{tabularx}
\begin{tabularx}{\textwidth}{X}
    \hspace{10pt}Designed and built data platform and backend APIs. Built and optimized bioinformatics pipelines.
    \begin{itemize}
        \itemsep\itemseppts
        \item[-] Acted as SME for bioinformatics tooling and pipelines development.
        \item[-] Leveraged Terraform to build and managed AWS infrastructure. Migrated existing resources into AWS ecosystem.
    \end{itemize}
\end{tabularx}

\begin{tabularx}{\textwidth}{L R}
    \normalsize\textit{Neuralink Corp.} & Fremont, CA \\
    \hspace{10pt}Infrastructure Engineer & February 2020 --- July 2021 \\
\end{tabularx}
\begin{tabularx}{\textwidth}{X}
    \hspace{10pt}Head of software infrastructure team. Led company-wide network, storage, compute, and security initiatives.
    \begin{itemize}
        \itemsep\itemseppts
        \item[-] Acted as SME for networking, storage, compute, and digital security, for both on-prem and AWS. Mentored both technical and non-technical team members in software development practices, SDLC, and developer resources.
        \item[-] Built and managed a hybrid on-prem and cloud infrastructure, with a mixture of EC2 / ECS / EKS in AWS, ESXi and K8S on-prem, and roughly 100 SFF bare metal servers supporting various research and manufacturing workloads.
        \item[-] Codified systems and services utilizing HashiCorp Packer, Terraform, and Vault, Helm, Ansible, Python, and GitLab.
        \item[-] Identified and remediated physical and digital security vulnerabilities in company facilities and systems. Acted as point of contact for security, and member of 3 party quorum handling company security architecture and design.
        \item[-] Managed team of 3 infrastructure engineers and IT specialists. Managed software and hardware vendor engagement.
    \end{itemize}
\end{tabularx}

\begin{tabularx}{\textwidth}{L R}
    \normalsize\textit{Cisco Systems Inc.} & Chicago, IL \\
    \hspace{10pt}Systems \& Software Engineer & September 2016 --- February 2020 \\
\end{tabularx}
\begin{tabularx}{\textwidth}{X}
    \hspace{10pt}Built out SOC data platform, and supported red / blue team initiatives.
    \begin{itemize}
        \itemsep\itemseppts
        \item[-] Developed services in Rust to ingest security-centric data for over 30k+ active virtual machines and devices. Deployed and managed a PostgreSQL database of findings with GraphQL access layer, allowing for rapid querying by SOC team members, and the identification and remediation of thousands of high-severity vulnerabilites.
        \item[-] Codified systems and services utilizing the entire HashiCorp stack, Ansible, Python, and GitLab. Deployed and maintained OpenStack and ESXi clusters, Ceph storage cluster, and network infrastructure.
        \item[-] Diagnosed exposure to critical software vulnerabilities of Cisco's labs globally, and facilitated the triage and remediation process by aligning vulnerable systems, and associated remediation processes, with organizational owners.
        \item[-] Provided application security architecture consulting to major healthcare providers and top 5 financial institutions.
    \end{itemize}
\end{tabularx}

\begin{tabularx}{\textwidth}{L R}
    \normalsize\textit{University of Chicago} & Chicago, IL \\
    \hspace{10pt}Software Engineer & September 2013 --- June 2016 \\
\end{tabularx}
\begin{tabularx}{\textwidth}{X}
    \hspace{10pt}Built internal backend systems, data access APIs, and analysis cluster / pipelines.
    \begin{itemize}
        \itemsep\itemseppts
        \item[-] Built data access REST APIs using Python Flask, and client CLI and libraries using C/C++, Python, and Go.
        \item[-] Build and managed on-prem infrastructure and deployment pipeline utilizing HashiCorp Consul and Saltstack.
        \item[-] Diagnosed flaws in the Ceph Object Gateway (radosgw) storage system, leading to corruption of $>$30\% of S3 objects. Analyzed $>$100TiB of RADOS objects and developed API middleware to repair errors in-line with requests, recovering 3 months of research and PiBs of analysis results.
    \end{itemize}
\end{tabularx}
